Methods_tidy

### 2019-04-08 Exploring/Tester_code/Methods.Rmd
housekeeping

save(SACTN_3yr, file = "Data/SACTN_3yr.RData")
```

@@

OISSTDir <- "~/Documents/Masters_2019/Data_SST"
OISST <- fread(paste0(OISSTDir, "/csvavhrr-only-v2-19810901-20180630.csv"),
            col.names = c("lon", "lat", "temp", "date"))

>>>>

# save(SACTN_3yr, file = "Data/SACTN_3yr.RData")
```

@@

OISSTDir <- "~/Documents/Masters_2019/Data_SST"
# OISST <- fread(paste0(OISSTDir, "/csvavhrr-only-v2-19810901-20180630.csv"),
#             col.names = c("lon", "lat", "temp", "date"))

### 2019-04-08 Exploring/Tester_code/Methods_tidy.Rmd
housekeeping

### Load site list SACTN data

Now to get to the data. The first step involves the loading of the site list. The statistical properties of the seawater temperature representing the South African coastline, such as the mean, minimum and maximum temperatures. These values vary among coastal sections due to the influence of the cold Benguala and warm Agulhas currents. Here we will only focus on the temperature data found along the west coast (wc) (i.e. sites influenced by the Benguela current, EBUS). The SACTN dataset comprise of 129 *in situ* coastal seawater temperatures derived from daily measurements over up to 40 years. The SACTN temperature dataset was compiled by measuring coastal temperatures at 129 sites along the coast of South Africa, daily from 1972 until 2017.

@@

Now we select only the sites occuring along the west coast. Thereafter, I include all the sites which had a time series of 10 years or greater. This yield a 2 rows of data for Paternoster. I removed the row of data obtained by the DEA, thus ending up with all of the data being obtained from SAWS in this dataset. I then exclude the sites that do not fall within the upwelling cell. Once those sites were removed, we have a total of 4 sites. These are: Port Nolloth, Lamberts Bay, Saldanna and Yzerfontein.

```{r}
site_list_sub <- site_list %>% 
  filter(coast == "wc")

SACTN_daily_wc <- site_list_sub %>% 
  filter(length >= 3650)

upwelling_sites <- SACTN_daily_wc[-6,] # Here we had two rows of data for Paternoster; i removed the DEA row: All data here are now collected by SAWS 
upwelling_sites <- upwelling_sites[-10:-14,] # Here i remove the sites that does not fall within the upwelling cell

# Here I find a time series with the data occuring in the most recent years
upwelling_sites <- upwelling_sites[c(-2, -3, -5, -6, -8),] 
# save(upwelling_sites, file = "Data/upwelling_sites.RData")

SACTN_daily_temps <- SACTN_daily_v4.2 %>% 
  left_join(site_list[,c(4,13)], by = "index") %>% 
  filter(index %in% upwelling_sites$index)
# save(SACTN_daily_temps, file = "SACTN_daily_temps.RData")

SACTN_daily_temps_indexsplit <- SACTN_daily_temps %>% 
  separate(index, into = c("site", "src"), sep = "/", remove = FALSE) %>% 
  dplyr::rename(insitu_temp = temp)

# save(SACTN_daily_temps_indexsplit, file = "Data/SACTN_daily_temps_indexsplit.RData")
```

@@

# SACTN_split <- SACTN_monthly(df = SACTN_daily_temps_indexsplit)
# save(SACTN_split, file = "SACTN_split.RData")
```

Find where different sites have overlapping time series within this `SACTN_split` dataset.

```{r}
load("~/Documents/Masters_2019/MastersProject/Data/SACTN_split.RData")

SACTN_3yr <- SACTN_split %>% 
  filter(year(date) %in% seq(2014, 2015)) %>% 
  drop_na() # Removing NA values within the dataset

save(SACTN_3yr, file = "Data/SACTN_3yr.RData")

insitu_temp_plot <- ggplot(data = SACTN_3yr, aes(x = date, y = insitu_temp, colour = site)) +
geom_line(aes(group = site)) +
labs(x = "", y = "Temperature (°C)") +
theme(axis.text.x = element_text(angle = 45)) +
#theme_linedraw() +
theme(legend.position = "top")

# ggsave(plot = insitu_temp_plot, filename = "Figures/insitu_temp.pdf")
```

@@

## MUR dataset

```{r}
MUR_Lamberts_Bay <- read_csv("Data/MUR_nearest5pixels/MUR_Lamberts Bay_SST_timeseries_5nearest.csv")
MUR_Port_Nolloth <- read_csv("Data/MUR_nearest5pixels/MUR_Port Nolloth_SST_timeseries_5nearest.csv")
MUR_Saldanha_Bay <- read_csv("Data/MUR_nearest5pixels/MUR_Saldanha Bay_SST_timeseries_5nearest.csv")
MUR_Yzerfontein <- read_csv("Data/MUR_nearest5pixels/MUR_Yzerfontein_SST_timeseries_5nearest.csv")

@@

MUR_SST$date <- (ymd(MUR_SST$date))
# save(MUR_SST, file = "Data/MUR_SST.RData")

@@

match_func <- function(df){
  match <- SACTN_3yr  %>%  
  left_join(df, by = c("site", "date")) %>% 
  na.trim()
  return(match)
}

insitu_MUR <- match_func(df = MUR_SST) %>%
  drop_na()

match_plot <- function(df){
  plot1 <- df %>% 
ggplot(aes(x = date, y = temp)) +
  geom_hline(aes(yintercept = mean(temp)), colour = "salmon") +
  geom_line() +
  facet_wrap(~ site, nrow = 2) +
  theme_bw()
  return(plot1)
}

MUR_plot <- match_plot(df = insitu_MUR)
mur_temp_plot <- ggplot(data = insitu_MUR, aes(x = date, y = temp, colour = site)) +
geom_line(aes(group = site)) +
labs(x = "", y = "Temperature (°C)") +
theme(axis.text.x = element_text(angle = 45)) +
#theme_linedraw() +
theme(legend.position = "top")

# ggsave(plot = mur_temp_plot, filename = "Figures/mur_temp_plot.pdf")

```

## OISST dataset

```{r}
# AVHRR <- read_csv("data/csvavhrr-only-v2-19810901-20180630.csv")

@@

## Matching the Insitu data with the OISST SST data

```{r}
insitu_OISST <- match_func(df = OISST_sites)
OISST_plot <- match_plot(df = insitu_OISST)

OISST_temp_plot <- ggplot(data = insitu_OISST, aes(x = date, y = temp, colour = site)) +
geom_line(aes(group = site)) +
labs(x = "", y = "Temperature (°C)") +
theme(axis.text.x = element_text(angle = 45)) +
# theme_linedraw() +
theme(legend.position = "top")
# ggsave(plot = OISST_temp_plot, filename = "Figures/OISST_temp_plot.pdf")
```

## G1SST dataset

```{r}
Lamberts_Bay <- read_csv("Data/G1SST_sub/Lamberts Bay_SST_timeseries_5nearest.csv")
Port_Nolloth <- read_csv("Data/G1SST_sub/Port Nolloth_SST_timeseries_5nearest.csv")
Saldanha_Bay <- read_csv("Data/G1SST_sub/Saldanha Bay_SST_timeseries_5nearest.csv")
Yzerfontein <- read_csv("Data/G1SST_sub/Yzerfontein_SST_timeseries_5nearest.csv")

G1SSTsub_SST <- rbind(Lamberts_Bay,Port_Nolloth, Saldanha_Bay, Yzerfontein) %>%
  dplyr::rename(site = station)

G1SSTsub_SST$date <- (ymd(G1SSTsub_SST$date))

# save(G1SSTsub_SST, file = "Data/G1SSTsub_SST.RData")
load("Data/G1SSTsub_SST.RData")

G1SSTsub_SST <- G1SSTsub_SST %>% 
  drop_na()

G1SSTsub_SST <- G1SSTsub_SST %>% 
  dplyr::rename(temp = nearest1)

insitu_G1SST <- match_func(df = G1SSTsub_SST) %>%
  drop_na()
G1SST_plot <- match_plot(df = insitu_G1SST )

G1SST_temp_plot <- ggplot(data = insitu_G1SST, aes(x = date, y = temp, colour = site)) +
geom_line(aes(group = site)) +
labs(x = "", y = "Temperature (°C)") +
theme(axis.text.x = element_text(angle = 45)) +
# theme_linedraw() +
theme(legend.position = "top")
# ggsave(plot = G1SST_temp_plot, filename = "Figures/G1SST_temp_plot.pdf")
```

@@

@@

@@

>>>>

### Load site list SACTN data
Now to get to the data. The first step involves the loading of the site list. The statistical properties of the seawater temperature representing the South African coastline, such as the mean, minimum and maximum temperatures. These values vary among coastal sections due to the influence of the cold Benguala and warm Agulhas currents. Here we will only focus on the temperature data found along the west coast (wc) (i.e. sites influenced by the Benguela current, EBUS). The SACTN dataset comprise of 129 *in situ* coastal seawater temperatures derived from daily measurements over up to 40 years. The SACTN temperature dataset was compiled by measuring coastal temperatures at 129 sites along the coast of South Africa, daily from 1972 until 2017.

@@

## Selecting the sites and creating new *in situ* datasets
Now we select only the sites occuring along the west coast. Thereafter, I include all the sites which had a time series of 10 years or greater.

```{r}
# site_list_sub <- site_list %>%
#   filter(coast == "wc")
# 
# SACTN_daily_wc <- site_list_sub %>%
#   filter(length >= 3650)
# 
# upwelling_sites <- SACTN_daily_wc[-6,] # Here we had two rows of data for Paternoster; i removed the DEA row: All data here are now collected by SAWS
# upwelling_sites <- upwelling_sites[-10:-14,] # Here i remove the sites that does not fall within the upwelling cell
# 
# # Here I find a time series with the data occuring in the most recent years
# UC_1 <- upwelling_sites[c(-2, -3, -5, -6, -8),]
# save(UC_1, file = "Data/UC_1.RData")
# 
# SACTN_daily_temps <- SACTN_daily_v4.2 %>%
#   left_join(site_list[,c(4,13)], by = "index") %>%
#   filter(index %in% upwelling_sites$index)
# # save(SACTN_daily_temps, file = "SACTN_daily_temps.RData")
# 
# SACTN_US1 <- SACTN_daily_temps %>%
#   separate(index, into = c("site", "src"), sep = "/", remove = FALSE) %>%
#   dplyr::rename(insitu_temp = temp)
# save(SACTN_US1, file = "Data/SACTN_US1.RData")

# site_list_sub_UC <- site_list %>%
#   filter(coast == "wc")
# 
# SACTN_daily_wc <- site_list_sub_UC %>%
#   filter(length >= 3650)
# 
# upwelling_sites_UC <- SACTN_daily_wc[-1:-8,]
# UC_2 <- upwelling_sites_UC[c(-2,-5),] # New sites falling within the upwelling cell before yzerfontein
# save(UC_2, file = "Data/UC_2.RData")

# SACTN_daily_temps_UC <- SACTN_daily_v4.2 %>%
#   left_join(site_list[,c(4,13)], by = "index") %>%
#   filter(index %in% upwelling_sites_UC$index)
# # save(SACTN_daily_temps, file = "SACTN_daily_temps.RData")
# 
# SACTN_US2 <- SACTN_daily_temps_UC %>%
#   separate(index, into = c("site", "src"), sep = "/", remove = FALSE) %>%
#   dplyr::rename(insitu_temp = temp)
# 
# save(SACTN_US2, file = "Data/SACTN_US2.RData")
```

@@

# SACTN_split_US1 <- SACTN_monthly(df = SACTN_US1)
# SACTN_split_US2 <- SACTN_monthly(df = SACTN_US2)
# save(SACTN_split_US1, file = "SACTN_split_US1.RData")
# save(SACTN_split_US2, file = "SACTN_split_US2.RData")
```

Find where different sites have overlapping time series within this `SACTN_split` dataset. Finding a long time series

```{r}
load("~/Documents/Masters_2019/MastersProject/Data/SACTN_split_US1.RData")
load("~/Documents/Masters_2019/MastersProject/Data/SACTN_split_US2.RData")

# Find a period where each of the sites within SACTN_US1 and SACTN_US2 that overlap. See dataset UC_1.RData and UC_2.RData

UC1 <- SACTN_split_US1 %>% 
  filter(year(date) %in% seq(1992, 2016)) %>% # see datsets UC_1.RData
  drop_na() # Removing NA values within the dataset

# Find a period where each of the sites within SACTN_US1 and SACTN_US2 that overlap
UC2 <- SACTN_split_US2 %>% 
  filter(year(date) %in% seq(1992, 2016)) %>% # see datsets UC_2.RData
  drop_na() # Removing NA values within the dataset

UC1 <- temp_plot(df = UC1)
UC2 <- temp_plot(df = UC2)

temp_plot <- function(df){
  plot <- ggplot(data = df, aes(x = date, y = insitu_temp, colour = site)) +
    geom_line(aes(group = site)) +
    labs(x = "", y = "Temperature (°C)") +
    theme(axis.text.x = element_text(angle = 45)) +
    theme(legend.position = "top")
}

UC1 <- temp_plot(df = UC1)
UC2 <- temp_plot(df = UC2)
```

@@

## MUR dataset
```{r}
MUR_Lamberts_Bay <- read_csv("Data/MUR_nearest5pixels/MUR_Lamberts Bay_SST_timeseries_5nearest.csv")
MUR_Port_Nolloth <- read_csv("Data/MUR_nearest5pixels/MUR_Port Nolloth_SST_timeseries_5nearest.csv")
MUR_Saldanha_Bay <- read_csv("Data/MUR_nearest5pixels/MUR_Saldanha Bay_SST_timeseries_5nearest.csv")
MUR_Yzerfontein <- read_csv("Data/MUR_nearest5pixels/MUR_Yzerfontein_SST_timeseries_5nearest.csv")

@@

MUR_SST$date <- (ymd(MUR_SST$date))
#save(MUR_SST, file = "Data/MUR_SST.RData")

@@

match_func <- function(df){
  match <- SACTN_split_US1  %>%  
  left_join(df, by = c("site", "date")) %>% 
  na.trim()
  return(match)
}
insitu_MUR <- match_func(df = MUR_SST) %>%
  drop_na()

match_plot <- function(df){
  plot1 <- df %>% 
ggplot(aes(x = date, y = temp)) +
  geom_hline(aes(yintercept = mean(temp)), colour = "salmon") +
  geom_line() +
  facet_wrap(~ site, nrow = 2) +
  theme_bw()
  return(plot1)
}
MUR_plot <- match_plot(df = insitu_MUR)

temp_plot <- function(df){
  temp_plot <- df %>% 
  ggplot(aes(x = date, y = temp, colour = site)) +
    geom_line(aes(group = site)) +
    labs(x = "", y = "Temperature (°C)") +
    theme(axis.text.x = element_text(angle = 45)) +
    theme(legend.position = "top")
}
MUR_plot <- temp_plot(df = insitu_MUR)
```

## OISST dataset
```{r}
# AVHRR <- read_csv("data/csvavhrr-only-v2-19810901-20180630.csv")

@@

## Matching the Insitu data with the OISST SST data
```{r}
insitu_OISST <- match_func(df = OISST_sites)
OISST_plot <- match_plot(df = insitu_OISST)
OISST_temp_plot <- temp_plot(df = insitu_OISST)
```

## G1SST dataset
```{r}
# Lamberts_Bay <- read_csv("Data/G1SST_sub/Lamberts Bay_SST_timeseries_5nearest.csv")
# Port_Nolloth <- read_csv("Data/G1SST_sub/Port Nolloth_SST_timeseries_5nearest.csv")
# Saldanha_Bay <- read_csv("Data/G1SST_sub/Saldanha Bay_SST_timeseries_5nearest.csv")
# Yzerfontein <- read_csv("Data/G1SST_sub/Yzerfontein_SST_timeseries_5nearest.csv")
# 
# G1SSTsub_SST <- rbind(Lamberts_Bay,Port_Nolloth, Saldanha_Bay, Yzerfontein) %>%
#   dplyr::rename(site = station)
# 
# G1SSTsub_SST$date <- (ymd(G1SSTsub_SST$date))
# # save(G1SSTsub_SST, file = "Data/G1SSTsub_SST.RData")

load("Data/G1SSTsub_SST.RData")

G1SSTsub_SST <- G1SSTsub_SST %>% 
  drop_na() %>% 
  dplyr::rename(temp = nearest1)

insitu_G1SST <- match_func(df = G1SSTsub_SST) 
G1SST_plot <- match_plot(df = insitu_G1SST )
G1SST_temp_plot <- temp_plot(df = insitu_G1SST)
```

# K10
```{r}
# Lamberts_Bay <- read_csv("Data/K10/K10_Lamberts Bay_SST_timeseries_5nearest.csv")
# Port_Nolloth <- read_csv("Data/K10/K10_Port Nolloth_SST_timeseries_5nearest.csv")
# Saldanha_Bay <- read_csv("Data/K10/K10_Saldanha Bay_SST_timeseries_5nearest.csv")
# Yzerfontein <- read_csv("Data/K10/K10_Yzerfontein_SST_timeseries_5nearest.csv")
# 
# K10_SST <- rbind(Lamberts_Bay, Yzerfontein, Port_Nolloth, Saldanha_Bay) %>%
#   dplyr::rename(site = station)
# K10_SST$date <- (ymd(K10_SST$date))
# save(K10_SST, file = "Data/K10_SST.RData")

load("~/Documents/Masters_2019/MastersProject/Data/K10_SST.RData")
K10_SST <- K10_SST %>% 
  drop_na()
K10_SST <- K10_SST %>% 
  dplyr::rename(temp = nearest1)

insitu_K10 <- match_func(df = K10_SST) 
K10_plot <- match_plot(df = insitu_K10)
k10_temp_plot <- temp_plot(df = insitu_K10)
```

# K10

temp.d <- insitu_K10_SST %>% 
  dplyr::group_by(site, date) %>% 
  dplyr::summarise(temp = mean(temp, na.rm = T)) %>%
  dplyr::mutate(no = seq(1:n())) %>%
  dplyr::ungroup() %>% 
  dplyr::select(site, no, temp, date)

auto.arima(dplyr::filter(insitu_K10_SST, site == "Port Nolloth")[, "temp"], max.p = 3, max.q = 3, stationary = FALSE, 
           seasonal = FALSE)

for (i in 1:length(PN_wave)) {
  attributes(PN_wave[[i]]) <- c(attributes(PN_wave[[i]]), ref = names(PN_wave)[i])
}
# x <- PN_wave[[3]]
plot_fun <- function(x, plot_name = attributes(x)$ref) {
  png(filename = paste0("Figures/K10/",plot_name,"_wavelet.png"),
      width = 800, height = 600, units = "px", pointsize = 12, bg = "white")
  wt.image(x, siglvl = 0.05, col.contour = "black", color.key = "quantile",
           timelab = "Days", verbose = FALSE, useRaster = TRUE,
           periodlab = "Period", lwd = 1, graphics.reset = FALSE,
           main = plot_name)
  dev.off()
}
ldply(PN_wave, plot_fun)
```

# SACTN

@@

# OISST

@@

# MUR

@@

# G1SST
